Dense depth estimation from image pairs

### 2021-06-30 paper/paper.tex
nice

\subsection{Interpretation of the algorithm and its parameters}
We are left with many parameters: regularizer parameter $\lambda$, thresholding parameter $\theta$, chosen each iteration, and the number of iterations.
The performance of our method relies heavily on the choices of these values --- the preliminary results seen in figure \ref{cloud_computed}
were only achieved by manual adjustment. Although, in principle, we aim to globally optimize the original cost function \eqref{nonlinear_cost},
our final method of optimization can be reinterpreted as a step-based algorithm:
\begin{itemize}
    \item
\end{itemize}

>>>>

\subsection{Interpretation of the algorithm and its parameters}
We are left with many parameters: regularizer parameter $\lambda$, thresholding parameter $\theta$, chosen each iteration, and the number of iterations.
The performance of our method relies heavily on the choices of these values --- the preliminary results seen in figure \ref{cloud_computed}
were only achieved by manual adjustment. Although, in principle, we aim to globally optimize the original cost function \eqref{nonlinear_cost},
our final method of optimization can be reinterpreted as a step-based algorithm, outlined here:
\begin{enumerate}
    \item Choose regularizer parameter $\lambda$.
    \item Choose an initial value for splitting parameter $\theta$.
    \item Initialize a depth map (say, to a constant 3 meters).
    \item For each pixel in camera one, find the point on the ray which reprojects to the closest intensity in camera two.
          Update the depth map at this pixel to be the distance to that point.
    \item Regularization (smoothing) step. Solve the ROF model to smooth the noisy depth map.
    \item Repeat step 4, but additionally penalize changes to the depth map.
         (e.g., find the point on the ray which minimizes the sum of reprojection error and a quadratic function of the difference to the old depth value).
    \item Go to step 5, unless sufficiently many iterations have been completed.
\end{enumerate}
